Network Configuration Synthesis with Abstract Topologies

### 2016-11-12 paper/abstraction/paper.tex
move section 8 into 7
update templates to include bth incremental and concrete versions

  \begin{center}
  \includegraphics[width=.8\columnwidth]{figures/configs}  
  \end{center}
  \vspace{-1em}
  \caption{Spine template and concrete configurations.}
  \label{fig:bgp-configs}
\end{figure}

\section{Compilation}

The translation from the Product Graph to per-device configurations that run the distributed BGP protocol involves several ideas.

@@

%=====================================================
%
%
%  **Concretization**
%
%
%=====================================================

@@

\section{Properties}

>>>>

  \begin{center}
  \includegraphics[width=\columnwidth]{figures/configs}  
  \end{center}
  \vspace{-1em}
  \caption{Spine template and concrete configurations (left), and evolution friendly templates (right).}
  \label{fig:bgp-configs}
\end{figure}

\section{Template Generation}

The translation from the Product Graph to per-device templates that run the distributed BGP protocol involves several ideas.

@@

@@
